---
title: "SRF-2018-Code"
author: "Keane Flynn & Weston Slaughter"
date: "12/30/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Load Libraries
```{r}
library(dplyr)
library(readr)
library(tidyverse)
library(ggplot2)
```

#Productivity Data

##ChlA Data
```{r}
ChlA_Data_Porter <- 
  readr::read_csv(file = "ChlA-Data/ChlA-Data.csv",
                  col_types = "ccccdcddddddddc") %>%
  filter(Site == "Porter_Above") %>%
  group_by(Date_collected, Site_1)
ChlA_Data_Porter
```

###Summarized ChlA Data
```{r}
Summarized_ChlA_Data_Pool <- ChlA_Data_Porter %>%
  filter(Pool_or_Riffle == "pool") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_ChlA_area = mean(Chla_area))

Summarized_ChlA_Data_Riffle <- ChlA_Data_Porter %>%
  filter(Pool_or_Riffle == "riffle") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_ChlA_area = mean(Chla_area))
```

###Plotting ChlA vs Time (Pool)
```{r}
ChlA_Graph_Pool <- Summarized_ChlA_Data_Pool %>%
  ggplot(aes(x = Date_collected, y = mean_ChlA_area)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Chlorophyll-A Reading per Unit Area of Cobble") +
  ggtitle("Chlorophyll-A Measurements vs Time (Pool)")
ChlA_Graph_Pool
```

###Plotting ChlA vs Time (Riffle)
```{r}
ChlA_Graph_Riffle <- Summarized_ChlA_Data_Riffle %>%
  ggplot(aes(x = Date_collected, y = mean_ChlA_area)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Chlorophyll-A Reading per Unit Area of Cobble") +
  ggtitle("Chlorophyll-A Measurements vs Time (Riffle)")
ChlA_Graph_Riffle
```

##AFD Data
```{r}
AFD_Data_Porter <-
  readr::read_csv(file = "ChlA-Data/AFD-Data.csv",
                  col_types = "ccccdcddddddddc") %>%
  filter(Site == "Porter_Above") %>%
  group_by(Date_collected, Site_1) %>%
  select(Date_collected, Site_1, Cobble_SID, Pool_or_Riffle, Dry_Weight_g, AFD_Weight_g, Difference)
AFD_Data_Porter
```

###Summarizing AFD Data (Pool)
```{r}
Summarized_AFD_Data_Pool <- AFD_Data_Porter %>%
  filter(Pool_or_Riffle == "pool") %>%
  filter(!AFD_Weight_g == "NA") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_diff = mean(Difference))

Summarized_AFD_Data_Riffle <- AFD_Data_Porter %>%
  filter(Pool_or_Riffle == "riffle") %>%
  filter(!AFD_Weight_g == "NA") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_diff = mean(Difference))
```

###Plotting AFD vs Time (Pool)
```{r}
AFD_Graph_Pool <- Summarized_AFD_Data_Pool %>%
  ggplot(aes(x = Date_collected, y = mean_diff)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Ash Free Dry Mass (Grams)") +
  ggtitle("Ash Free Dry Mass Measurements vs Time (Pool)")
AFD_Graph_Pool
```

###Plotting AFD vs Time (Riffle)
```{r}
AFD_Graph_Riffle <- Summarized_AFD_Data_Riffle %>%
  ggplot(aes(x = Date_collected, y = mean_diff)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Ash Free Dry Mass (Grams)") +
  ggtitle("Ash Free Dry Mass Measurements vs Time (Riffle)")
AFD_Graph_Riffle
```

#Dissolved Oxygen Data
```{r}
DO_Data_Porter <-
  readr::read_csv(file = "Photosynthesis/2018-Photosynthesis.csv",
                  col_types = "ccccdcddddcdddcdddcdddcddddddcdddddd") %>%
  filter(Stream == "Porter") %>%
  mutate(Max_Depth_DO = (MaxDepth_DO1 + MaxDepth_DO2 + MaxDepth_DO3)/3) %>%
  select(Stream, Date, Site_Name, Site_Num, Pool_Riffle, Max_Depth_DO, Light_Do_s, Light_DO_e, Dark_Do_s, Dark_DO_e)
DO_Data_Porter
```

##Dissolved Oxygen (Pool)
```{r}
Summary_DO_Data_Porter_Pool <- DO_Data_Porter %>%
  group_by(Stream, Date, Site_Name, Site_Num) %>%
  summarise(Max_Depth_DO = mean(Max_Depth_DO), Light_Do_s = mean(Light_Do_s), Light_DO_e = mean(Light_DO_e), Dark_Do_s = mean(Dark_Do_s), Dark_DO_e = mean(Dark_DO_e)) %>%
  arrange(Date, Site_Num)
Summary_DO_Data_Porter_Pool
```

##Plotting Max Depth DO (Pool)
```{r}
Max_Depth_DO_Graph_Pool <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Max_Depth_DO)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Max_Depth_DO_Graph_Pool
```

##Plotting Light DO_s Data
```{r}
Light_DO_s_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Light_Do_s)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Light_DO_s_Graph
```

##Plotting Light DO_e Data
```{r}
Light_DO_e_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Light_DO_e)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Light_DO_e_Graph
```

##Plotting Dark DO_s Data
```{r}
Dark_DO_s_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Dark_Do_s)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Dark_DO_s_Graph
```

##Plotting Dark DO_e Data
```{r}
Dark_DO_e_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Dark_DO_e)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Dark_DO_e_Graph
```

#Electrofishing Data
```{r}
EFishing_Data <-
  readr::read_csv(file = "FishPopulation/EFishingData2018.csv",
                  col_types = "cccddddttddcdccdccdddddddcddddddddd") %>%
  filter(Stream == "Porter") %>%
  arrange(Date, Unit, Fish_Num, Pass_Num)
EFishing_Data

CombiningMovement_Efish <- EFishing_Data %>%
  filter(!PIT == "N/A")
```

#Movement Data
```{r}
PIT_Data <- 
  readr::read_csv(file = "FishPopulation/POR_MovementStudy.csv",
                  col_types = "cccctccccc") %>%
  mutate(PIT = str_extract(PITNumber, "06....")) %>%
  select(Species_Lookup, PIT, Date_Lookup, Date, Time, Site, HabitatType, UnitNumber, Survey, Comments)
PIT_Data
```

##Creating a Movement vs Flow Dataset
```{r}
EFish_Movement_Data <- left_join(PIT_Data, CombiningMovement_Efish, by = "PIT") %>%
  select(Species, PIT, Date_Lookup, Date.x, Time, Site, UnitNumber, Survey, Unit, Fish_Num_Per_Site, Fish_Num, Length_mm, Weight_g, Recapture, Fat_AVG, Comments) %>%
  mutate(Survey_tally = if_else(Survey == "ANT", 1, 0)) %>%
  group_by(Date.x) %>%
  mutate(Movement_tally = cumsum(Survey_tally)) %>%
  mutate(Max_Ping_Tally = max(Movement_tally))
EFish_Movement_Data

Flow_MovementData <- EFish_Movement_Data %>%
  distinct(Max_Ping_Tally) %>%
  left_join(Porter_FlowData, EFish_Movement_Data, by = c("Date.x" = "Date")) %>%
  arrange(X1) %>%
  select(Date.x, Max_Ping_Tally, avg_gpm)
Flow_MovementData
```
##Movement Data vs Flow Graph
```{r}
ggplot(Flow_MovementData) + geom_col(aes(x = Date.x, y = Max_Ping_Tally), width = 0.5) + geom_line(aes(x = Date.x, y = avg_gpm), group = 1)
```

#Hydrology Data
```{r}
Porter_FlowData <- 
  readr::read_csv("Hydrology/PorterCreek_AugmentationData.csv") %>%
  select(X1, Date, avg_gpm)
Porter_FlowData
```
