---
title: "SRF-2018-Code"
author: "Keane Flynn & Weston Slaughter"
date: "12/30/2018"
output: github_document
---

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```
##Load Libraries
```{r}
library(dplyr)
library(readr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(geometry)
library(rgl)
library(hypervolume)
library(zoo)
library(stringr)
```

#Productivity Data

##ChlA Data
```{r}
ChlA_Data_Porter <- 
  readr::read_csv(file = "ChlA-Data/ChlA-Data.csv",
                  col_types = "ccccdcddddddddc") %>%
  filter(Site == "Porter_Above") %>%
  group_by(Date_collected, Site_1)
ChlA_Data_Porter
```

###Summarized ChlA Data
```{r}
Summarized_ChlA_Data_Pool <- ChlA_Data_Porter %>%
  filter(Pool_or_Riffle == "pool") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_ChlA_area = mean(Chla_area))

Summarized_ChlA_Data_Riffle <- ChlA_Data_Porter %>%
  filter(Pool_or_Riffle == "riffle") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_ChlA_area = mean(Chla_area))
```

###Plotting ChlA vs Time (Pool)
```{r}
ChlA_Graph_Pool <- Summarized_ChlA_Data_Pool %>%
  ggplot(aes(x = Date_collected, y = mean_ChlA_area)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Chlorophyll-A Reading per Unit Area of Cobble") +
  ggtitle("Chlorophyll-A Measurements vs Time (Pool)")
ChlA_Graph_Pool
```

###Plotting ChlA vs Time (Riffle)
```{r}
ChlA_Graph_Riffle <- Summarized_ChlA_Data_Riffle %>%
  ggplot(aes(x = Date_collected, y = mean_ChlA_area)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Chlorophyll-A Reading per Unit Area of Cobble") +
  ggtitle("Chlorophyll-A Measurements vs Time (Riffle)")
ChlA_Graph_Riffle
```

##AFD Data
```{r}
AFD_Data_Porter <-
  readr::read_csv(file = "ChlA-Data/AFD-Data.csv",
                  col_types = "ccccdcddddddddc") %>%
  filter(Site == "Porter_Above") %>%
  group_by(Date_collected, Site_1) %>%
  select(Date_collected, Site_1, Cobble_SID, Pool_or_Riffle, Dry_Weight_g, AFD_Weight_g, Difference)
AFD_Data_Porter
```

###Summarizing AFD Data (Pool)
```{r}
Summarized_AFD_Data_Pool <- AFD_Data_Porter %>%
  filter(Pool_or_Riffle == "pool") %>%
  filter(!AFD_Weight_g == "NA") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_diff = mean(Difference))

Summarized_AFD_Data_Riffle <- AFD_Data_Porter %>%
  filter(Pool_or_Riffle == "riffle") %>%
  filter(!AFD_Weight_g == "NA") %>%
  group_by(Date_collected, Site_1) %>%
  summarise(mean_diff = mean(Difference))
```

###Plotting AFD vs Time (Pool)
```{r}
AFD_Graph_Pool <- Summarized_AFD_Data_Pool %>%
  ggplot(aes(x = Date_collected, y = mean_diff)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Ash Free Dry Mass (Grams)") +
  ggtitle("Ash Free Dry Mass Measurements vs Time (Pool)")
AFD_Graph_Pool
```

###Plotting AFD vs Time (Riffle)
```{r}
AFD_Graph_Riffle <- Summarized_AFD_Data_Riffle %>%
  ggplot(aes(x = Date_collected, y = mean_diff)) +
  geom_line(aes(group = Site_1, color = Site_1)) +
  geom_point(aes(shape = Site_1)) +
  labs(x = "Date", y = "Average Ash Free Dry Mass (Grams)") +
  ggtitle("Ash Free Dry Mass Measurements vs Time (Riffle)")
AFD_Graph_Riffle
```

#Dissolved Oxygen Data
```{r}
DO_Data_Porter <-
  readr::read_csv(file = "Photosynthesis/2018-Photosynthesis.csv",
                  col_types = "ccccdcddddcdddcdddcdddcddddddcdddddd") %>%
  filter(Stream == "Porter") %>%
  mutate(Max_Depth_DO = (MaxDepth_DO1 + MaxDepth_DO2 + MaxDepth_DO3)/3) %>%
  select(Stream, Date, Site_Name, Site_Num, Pool_Riffle, Max_Depth_DO, Light_Do_s, Light_DO_e, Dark_Do_s, Dark_DO_e)
DO_Data_Porter
```

##Dissolved Oxygen (Pool)
```{r}
Summary_DO_Data_Porter_Pool <- DO_Data_Porter %>%
  group_by(Stream, Date, Site_Name, Site_Num) %>%
  summarise(Max_Depth_DO = mean(Max_Depth_DO), Light_Do_s = mean(Light_Do_s), Light_DO_e = mean(Light_DO_e), Dark_Do_s = mean(Dark_Do_s), Dark_DO_e = mean(Dark_DO_e)) %>%
  arrange(Date, Site_Num)
Summary_DO_Data_Porter_Pool
```

##Plotting Max Depth DO (Pool)
```{r}
Max_Depth_DO_Graph_Pool <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Max_Depth_DO)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Max_Depth_DO_Graph_Pool
```

##Plotting Light DO_s Data
```{r}
Light_DO_s_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Light_Do_s)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Light_DO_s_Graph
```

##Plotting Light DO_e Data
```{r}
Light_DO_e_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Light_DO_e)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Light_DO_e_Graph
```

##Plotting Dark DO_s Data
```{r}
Dark_DO_s_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Dark_Do_s)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Dark_DO_s_Graph
```

##Plotting Dark DO_e Data
```{r}
Dark_DO_e_Graph <- Summary_DO_Data_Porter_Pool %>%
  ggplot(aes(Date, Dark_DO_e)) +
  geom_line(aes(group = Site_Name, color = Site_Name)) +
  geom_point(aes(shape = Site_Name))
Dark_DO_e_Graph
```

#Electrofishing Data
```{r}
EFishing_Data <-
  readr::read_csv(file = "FishPopulation/EFishingData2018.csv",
                  col_types = "cccddddttddcdccdccdddddddcddddddddd") %>%
  filter(Stream == "Porter") %>%
  arrange(Date, Unit, Fish_Num, Pass_Num)
EFishing_Data

CombiningMovement_Efish <- EFishing_Data %>%
  filter(!PIT == "N/A")
```

#TU Hydrology Data
```{r}
Porter_FlowData <-
  readr::read_csv("Hydrology/PorterCreek_FlowData_TU.csv") %>%
  mutate(Date = str_extract(SampleDate, "\\d......")) %>%
  group_by(Date) %>%
  summarise(Streamflow_cfs = mean(Streamflow_cfs)) %>%
  mutate(Streamflow_gpm = Streamflow_cfs*448) %>%
  mutate(Date = str_extract(Date, "[0-9]{1,2}/[0-9]{1,2}/18")) %>%
  filter(!Date == "NA") 
Porter_FlowData
```

#Augmentation Data
```{r}
Porter_AugmentationData <- 
  readr::read_csv("Hydrology/PorterCreek_AugmentationData.csv") %>%
  select(X1, Date, avg_gpm)
Porter_AugmentationData
```

#Movement Data
```{r}
PIT_Data <- 
  readr::read_csv(file = "FishPopulation/POR_MovementStudy.csv",
                  col_types = "cccctccccc") %>%
  mutate(PIT = str_extract(PITNumber, "06....")) %>%
  select(Species_Lookup, PIT, Date_Lookup, Date, Time, Site, HabitatType, UnitNumber, Survey, Comments) 
PIT_Data
```

##Creating a Movement vs Augmentation Dataset
```{r}
EFish_Movement_Data <- left_join(PIT_Data, CombiningMovement_Efish, by = "PIT") %>%
  select(Species, PIT, Date_Lookup, Date.x, Time, Site, UnitNumber, Survey, Unit, Fish_Num_Per_Site, Fish_Num, Length_mm, Weight_g, Recapture, Fat_AVG, Comments) %>%
  mutate(Survey_tally = if_else(Survey == "ANT", 1, 0)) %>%
  group_by(Date.x) %>%
  mutate(Movement_tally = cumsum(Survey_tally)) %>%
  mutate(Max_Ping_Tally = max(Movement_tally)) %>%
  arrange(Date.x, Time) %>%
  filter(!Species == "Cottus_spp")
EFish_Movement_Data

Augmentation_MovementData <- EFish_Movement_Data %>%
  distinct(Max_Ping_Tally) %>%
  left_join(Porter_AugmentationData, EFish_Movement_Data, by = c("Date.x" = "Date")) %>%
  arrange(X1) %>%
  select(X1, Date.x, Max_Ping_Tally, avg_gpm) %>%
  filter(!X1 == "NA") 
  names(Augmentation_MovementData)[2] <- "Date"
Augmentation_MovementData 
Augmentation_MovementData$Date <- as.Date(Augmentation_MovementData$Date, "%m/%d/%Y")
```

###Movement Data vs Flow Graph
```{r}
ggplot(Augmentation_MovementData) + 
  geom_col(aes(x = Date, y = Max_Ping_Tally), width = 0.5, fill = "blue") + 
  geom_line(aes(x = Date, y = avg_gpm/5), group = 1, color = "red") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Augmentation (GPM)")) + 
  labs(x = "Date", y = "Salmonid PIT Movement Pings") + 
  ggtitle("Augmentation vs Interpool Movement Relationship") +
  theme(axis.text.y.right = element_text(colour="red"), axis.text.y.left = element_text(colour="blue"), axis.title.y.right = element_text(color = "red"), axis.title.y.left = element_text(color = "blue"))
```

##Movement Data vs Discharge Data
```{r}
Flow_MovementData <- EFish_Movement_Data %>%
  distinct(Max_Ping_Tally) %>%
  left_join(Porter_FlowData, EFish_Movement_Data, by = c("Date.x" = "Date")) %>%
  select(Date.x, Max_Ping_Tally, Streamflow_gpm) %>%
  filter(!Date.x == "NA")
  names(Flow_MovementData)[1] <- "Date"
Flow_MovementData
Flow_MovementData$Date <- as.Date(Flow_MovementData$Date, "%m/%d/%Y")
```

###Movement Data vs Discharge Data
```{r}
ggplot(Flow_MovementData) + 
  geom_col(aes(x = Date, y = Max_Ping_Tally), width = 0.5, fill = "blue") + 
  geom_line(aes(x = Date, y = Streamflow_gpm/5), group = 1, color = "red") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Discharge (GPM)")) + 
  labs(x = "Date", y = "Salmonid PIT Movement Pings") + 
  ggtitle("Discharge vs Interpool Movement Relationship") +
  theme(axis.text.y.right = element_text(colour="red"), axis.text.y.left = element_text(colour="blue"), axis.title.y.right = element_text(color = "red"), axis.title.y.left = element_text(color = "blue"))
```

#VidSync Data
This section of the code is devoted to importing, analyzing, and creating correlations with 3-D Videogrammetry data collected using VidSync from the summer of 2018 on Porter Creek. This is my child and I will keep it neat.

##Importing Data
###Pre-Augmentation
```{r}
GolfBall_VidSync_Pre <- 
  readr::read_csv(file = "VidSync-Data/PreAugmentation/Porter_BACI_GolfBall_30June2018_Part3.csv",
           skip = 2,
                    col_names = c("objects", "event", "timecode", "time", "X", "Y", "Z", "pld_error", "projection_error", "nearest_camera_distance", "screen_coordinates"),
                    col_types = "cccdddddddd")

HalfTire_VidSync_Pre <-
  readr::read_csv(file = "VidSync-Data/PreAugmentation/Porter_BACI_HalfTire_29June2018_Part2.csv",
           skip = 2,
                    col_names = c("objects", "event", "timecode", "time", "X", "Y", "Z", "pld_error", "projection_error", "nearest_camera_distance", "screen_coordinates"),
                    col_types = "cccdddddddd")

RoachRun_VidSync_Pre <-
  readr::read_csv(file = "VidSync-Data/PreAugmentation/Porter_BACI_RoachRun_29June2018_Part3.csv",
           skip = 2,
                    col_names = c("objects", "event", "timecode", "time", "X", "Y", "Z", "pld_error", "projection_error", "nearest_camera_distance", "screen_coordinates"),
                    col_types = "cccdddddddd")
```
###Post-Augmentation
```{r}
GolfBall_VidSync_Post <-
  readr::read_csv(file = "VidSync-Data/PostAugmentation/Porter_BACI_Golfball_6July2018_Part1.csv",
           skip = 2,
                    col_names = c("objects", "event", "timecode", "time", "X", "Y", "Z", "pld_error", "projection_error", "nearest_camera_distance", "screen_coordinates"),
                    col_types = "cccdddddddd")

RoachRun_VidSync_Post <-
  readr::read_csv(file = "VidSync-Data/PostAugmentation/Porter_BACI_RoachRun_5July2018_Part1.csv",
           skip = 2,
                    col_names = c("objects", "event", "timecode", "time", "X", "Y", "Z", "pld_error", "projection_error", "nearest_camera_distance", "screen_coordinates"),
                    col_types = "cccdddddddd")

HalfTire_VidSync_Post <- readr::read_csv(file = "VidSync-Data/PostAugmentation/Porter_BACI_HalfTire_5July2018_Part3.csv",
           skip = 2,
                    col_names = c("objects", "event", "timecode", "time", "X", "Y", "Z", "pld_error", "projection_error", "nearest_camera_distance", "screen_coordinates"),
                    col_types = "cccdddddddd")
```
##Analyzation
We will be analyzing functions such as NND, distance travelled per time (cm/s), distance to forage attempt (DFA), proportion of forage types, volume occupied, overlap in forage volumes, etc.
###Nearest Neighbor Distance (NND)
This will use the three dimensional distance formula to look at nearest neighbor at any given time during the subsample rather than the average centroid point.
####Pre-Augmentation
```{r}
nnd_GolfBall_Pre <- GolfBall_VidSync_Pre %>%
  ungroup() %>%
  filter(grepl("^Subsample.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  filter(!grepl("^Attack.*", event)) %>%
  filter(!grepl("^Nip.*", event)) %>%
  mutate(Fish_ID = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  dplyr::select(Fish_ID, event, time, X, Y, Z) %>%
  arrange(time) %>%
  group_by(time) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(nnd = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  group_by(time) %>%
  filter(!nnd == 0) %>%
  filter(nnd == min(nnd)) %>%
  ungroup() %>%
  group_by(Fish_ID) %>%
  summarise(median_nnd = median(nnd))
nnd_GolfBall_Pre

nnd_HalfTire_Pre <- HalfTire_VidSync_Pre %>%
  ungroup() %>%
  filter(grepl("^Subsample.*", objects)) %>%
  mutate(Fish_ID = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  dplyr::select(Fish_ID, time, X, Y, Z) %>%
  arrange(time) %>%
  group_by(time) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(nnd = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  group_by(time) %>%
  filter(!nnd == 0) %>%
  filter(nnd == min(nnd)) %>%
  ungroup() %>%
  group_by(Fish_ID) %>%
  summarise(median_nnd = median(nnd))
nnd_HalfTire_Pre
```
####Post-Augmentation
```{r}
nnd_GolfBall_Post <- GolfBall_VidSync_Post %>%
  ungroup() %>%
  filter(grepl("^Subsample.*", objects)) %>%
  mutate(Fish_ID = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  dplyr::select(Fish_ID, event, time, X, Y, Z) %>%
  arrange(time) %>%
  group_by(time) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(nnd = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  group_by(time) %>%
  filter(!nnd == 0) %>%
  filter(nnd == min(nnd)) %>%
  ungroup() %>%
  group_by(Fish_ID) #%>%
  #summarise(median_nnd = median(nnd))
nnd_GolfBall_Post

nnd_HalfTire_Post <- HalfTire_VidSync_Post %>%
  ungroup() %>%
  filter(grepl("^Subsample.*", objects)) %>%
  mutate(Fish_ID = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  dplyr::select(Fish_ID, time, X, Y, Z) %>%
  arrange(time) %>%
  group_by(time) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(nnd = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  group_by(time) %>%
  filter(!nnd == 0) %>%
  filter(nnd == min(nnd)) %>%
  ungroup() %>%
  group_by(Fish_ID) %>%
  summarise(median_nnd = median(nnd))
nnd_HalfTire_Post

nnd_RoachRun_Pre <- RoachRun_VidSync_Pre %>%
  ungroup() %>%
  filter(grepl("^Subsample.*", objects)) %>%
  mutate(Fish_ID = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  dplyr::select(Fish_ID, time, X, Y, Z) %>%
  arrange(time) %>%
  group_by(time) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(nnd = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  group_by(time) %>%
  filter(!nnd == 0) %>%
  filter(nnd == min(nnd)) %>%
  ungroup() %>%
  group_by(Fish_ID) %>%
  summarise(median_nnd = median(nnd))
nnd_RoachRun_Pre
```
###Distance Travelled per Time (cm/s)
This will use the three dimensional distance formula divided by time.
####Pre-Augmentation
```{r}
GolfBall_DistPerTime_Pre <- GolfBall_VidSync_Pre %>%
  arrange(objects, time) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = as.numeric(str_extract(objects, "\\d"))) %>%
  mutate(index = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(fish_distance_travelled_cm = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  mutate(date = as.Date("2018-06-30")) %>%
  mutate(BACI_date = as.Date("2018-06-29")) %>%
  mutate(site = "18.3") %>%
  mutate(event = "Before") %>%
  group_by(index) %>%
  mutate(distance_cm_per_sec = fish_distance_travelled_cm /(time - lag(time, default = first(time)))) %>%
  filter(!distance_cm_per_sec == Inf) %>%
  mutate(DistPerTime_Median = median(fish_distance_travelled_cm)) %>%
  mutate(DistPerTime_Mean = mean(fish_distance_travelled_cm)) %>%
  dplyr::select(date, BACI_date, event, site, subsample, index, DistPerTime_Median, DistPerTime_Mean) %>%
  distinct() %>%
  arrange(as.numeric(index))


HalfTire_DistPerTime_Pre <- HalfTire_VidSync_Pre %>%
  arrange(objects, time) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = as.numeric(str_extract(objects, "\\d"))) %>%
  mutate(index = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(fish_distance_travelled_cm = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  mutate(date = as.Date("2018-06-29")) %>%
  mutate(BACI_date = as.Date("2018-06-29")) %>%
  mutate(site = "18.8") %>%
  mutate(event = "Before") %>%
  group_by(index) %>%
  mutate(distance_cm_per_sec = fish_distance_travelled_cm /(time - lag(time, default = first(time)))) %>%
  filter(!distance_cm_per_sec == Inf) %>%
  mutate(DistPerTime_Median = median(fish_distance_travelled_cm)) %>%
  mutate(DistPerTime_Mean = mean(fish_distance_travelled_cm)) %>%
  dplyr::select(date, BACI_date, event, site, subsample, index, DistPerTime_Median, DistPerTime_Mean) %>%
  distinct() %>%
  arrange(as.numeric(index))
  

RoachRun_DistPerTime_Pre <- RoachRun_VidSync_Pre %>%
  arrange(objects, time) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = as.numeric(str_extract(objects, "\\d"))) %>%
  mutate(index = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(fish_distance_travelled_cm = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  mutate(date = as.Date("2018-06-29")) %>%
  mutate(BACI_date = as.Date("2018-06-29")) %>%
  mutate(site = "18.5") %>%
  mutate(event = "Before") %>%
  group_by(index) %>%
  mutate(distance_cm_per_sec = fish_distance_travelled_cm /(time - lag(time, default = first(time)))) %>%
  filter(!distance_cm_per_sec == Inf) %>%
  mutate(DistPerTime_Median = median(fish_distance_travelled_cm)) %>%
  mutate(DistPerTime_Mean = mean(fish_distance_travelled_cm)) %>%
  dplyr::select(date, BACI_date, event, site, subsample, index, DistPerTime_Median, DistPerTime_Mean) %>%
  distinct() %>%
  arrange(as.numeric(index))
```
####Post-Augmentation
```{r}
GolfBall_DistPerTime_Post <- GolfBall_VidSync_Post %>%
  arrange(objects, time) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = as.numeric(str_extract(objects, "\\d"))) %>%
  mutate(index = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(fish_distance_travelled_cm = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  mutate(date = as.Date("2018-07-06")) %>%
  mutate(BACI_date = as.Date("2018-07-05")) %>%
  mutate(site = "18.3") %>%
  mutate(event = "After") %>%
  group_by(index) %>%
  mutate(distance_cm_per_sec = fish_distance_travelled_cm /(time - lag(time, default = first(time)))) %>%
  filter(!distance_cm_per_sec == Inf) %>%
  mutate(DistPerTime_Median = median(fish_distance_travelled_cm)) %>%
  mutate(DistPerTime_Mean = mean(fish_distance_travelled_cm)) %>%
  dplyr::select(date, BACI_date, event, site, subsample, index, DistPerTime_Median, DistPerTime_Mean) %>%
  distinct() %>%
  arrange(as.numeric(index))


RoachRun_DistPerTime_Post <- RoachRun_VidSync_Post %>%
  arrange(objects, time) %>% 
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = as.numeric(str_extract(objects, "\\d"))) %>%
  mutate(index = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(fish_distance_travelled_cm = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  mutate(date = as.Date("2018-07-05")) %>%
  mutate(BACI_date = as.Date("2018-07-05")) %>%
  mutate(site = "18.5") %>%
  mutate(event = "After") %>%
  group_by(index) %>%
  mutate(distance_cm_per_sec = fish_distance_travelled_cm /(time - lag(time, default = first(time)))) %>%
  filter(!distance_cm_per_sec == Inf) %>%
  mutate(DistPerTime_Median = median(fish_distance_travelled_cm)) %>%
  mutate(DistPerTime_Mean = mean(fish_distance_travelled_cm)) %>%
  dplyr::select(date, BACI_date, event, site, subsample, index, DistPerTime_Median, DistPerTime_Mean) %>%
  distinct() %>%
  arrange(as.numeric(index))

HalfTire_DistPerTime_Post <- HalfTire_VidSync_Post %>%
  arrange(objects, time) %>% 
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = as.numeric(str_extract(objects, "\\d"))) %>%
  mutate(index = as.numeric(str_extract(objects, "\\h\\d{1,2}"))) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  mutate(distance_travelled_X_cm = X - lag(X, default = first(X))) %>%
  mutate(distance_travelled_Y_cm = Y - lag(Y, default = first(Y))) %>%
  mutate(distance_travelled_Z_cm = Z - lag(Z, default = first(Z))) %>%
  mutate(fish_distance_travelled_cm = sqrt((distance_travelled_X_cm)^2
                                        + (distance_travelled_Y_cm)^2
                                        + (distance_travelled_Z_cm)^2)) %>%
  mutate(date = as.Date("2018-07-05")) %>%
  mutate(BACI_date = as.Date("2018-07-05")) %>%
  mutate(site = "18.8") %>%
  mutate(event = "After") %>%
  group_by(index) %>%
  mutate(distance_cm_per_sec = fish_distance_travelled_cm /(time - lag(time, default = first(time)))) %>%
  filter(!distance_cm_per_sec == Inf) %>%
  mutate(DistPerTime_Median = median(fish_distance_travelled_cm)) %>%
  mutate(DistPerTime_Mean = mean(fish_distance_travelled_cm)) %>%
  dplyr::select(date, BACI_date, event, site, subsample, index, DistPerTime_Median, DistPerTime_Mean) %>%
  distinct() %>%
  arrange(as.numeric(index))

MovementPerTime_Data <-
bind_rows(RoachRun_DistPerTime_Pre, RoachRun_DistPerTime_Post, GolfBall_DistPerTime_Pre, GolfBall_DistPerTime_Post, HalfTire_DistPerTime_Pre, HalfTire_DistPerTime_Post) %>%
  mutate(ID = 1) %>% 
  group_by(ID) %>%
  mutate(unique_ID = cumsum(ID)) %>%
  select(date, BACI_date, event, site, unique_ID, subsample, index, DistPerTime_Median, DistPerTime_Mean)
MovementPerTime_Data
```
###Distance to Forage Attempt (DFA)
Finding the centroid point then looking at the average distance to each subsequent point taken in the subsample and taking the average.

####Pre-Augmentation
```{r}

```
####Post-Augmentation
```{r}

```
###Proportion of Forage Types
Breaking down the proportion of each type of forage event and how it changes throughout the study period.

####Pre-Augmentation
```{r}

```
####Post-Augmentation
```{r}

```
###Volume Occupied
Using Delaunay Triangulation to calculate the volume each fish is occupying during each subsample.

####Pre-Augmentation
```{r}
GolfBall_Volume_Pre <- GolfBall_VidSync_Pre %>%
  arrange(objects) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = str_extract(objects, "\\d")) %>%
  mutate(index = str_extract(objects, "\\h\\d{1,2}")) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  transform(index = as.numeric(index),
            subsample = as.numeric(subsample)) %>%
  arrange(subsample, index, time) %>%
  select(subsample, index, X, Y, Z) %>%
  arrange(subsample, index)

for (i in 1:13) {
  if (i == 3) {
    next
  }
  if (i == 10) {
    next
  }
  GB_Pre_Filename <- paste("GB_Vol_Pre_", toString(i), sep = "")
  GolfBall_Volume_Pre %>%
    filter(index == i) %>%
    select(X, Y, Z) %>%
    as.matrix() %>%
    convhulln("FA") %>%
    print()
}

HalfTire_Volume_Pre <- HalfTire_VidSync_Pre %>%
  arrange(objects) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = str_extract(objects, "\\d")) %>%
  mutate(index = str_extract(objects, "\\h\\d{1,2}")) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  transform(index = as.numeric(index),
            subsample = as.numeric(subsample)) %>%
  arrange(subsample, index, time) %>%
  select(subsample, index, X, Y, Z) %>%
  arrange(subsample, index)

for (i in 1:8) {
  HalfTire_Volume_Pre %>%
    filter(index == i) %>%
    select(X, Y, Z) %>%
    as.matrix() %>%
    convhulln("FA") %>%
    print()
}

RoachRun_Volume_Pre <- RoachRun_VidSync_Pre %>%
  arrange(objects) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = str_extract(objects, "\\d")) %>%
  mutate(index = str_extract(objects, "\\h\\d{1,2}")) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  transform(index = as.numeric(index),
            subsample = as.numeric(subsample)) %>%
  arrange(subsample, index, time) %>%
  select(subsample, index, X, Y, Z) %>%
  arrange(subsample, index)

for (i in 1:19) {
  if (i == 3) {
    next
  }
  if (i == 7) {
    next
  }
  if (i == 14) {
    next
  }
  if (i == 16) {
    next
  }
  RoachRun_Volume_Pre %>%
    filter(index == i) %>%
    select(X, Y, Z) %>%
    as.matrix() %>%
    convhulln("FA") %>%
    print()
}
```
####Post-Augmentation
```{r}
GolfBall_Volume_Post <- GolfBall_VidSync_Post %>%
  arrange(objects) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = str_extract(objects, "\\d")) %>%
  mutate(index = str_extract(objects, "\\h\\d{1,2}")) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  transform(index = as.numeric(index),
            subsample = as.numeric(subsample)) %>%
  arrange(subsample, index, time) %>%
  select(subsample, index, X, Y, Z) %>%
  arrange(subsample, index)

for (i in 1:6) {
  GolfBall_Volume_Post %>%
    filter(index == i) %>%
    select(X, Y, Z) %>%
    as.matrix() %>%
    convhulln("FA") %>%
    print()
}

RoachRun_Volume_Post <- RoachRun_VidSync_Post %>%
  arrange(objects) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = str_extract(objects, "\\d")) %>%
  mutate(index = str_extract(objects, "\\h\\d{1,2}")) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  transform(index = as.numeric(index),
            subsample = as.numeric(subsample)) %>%
  arrange(subsample, index, time) %>%
  select(subsample, index, X, Y, Z) %>%
  arrange(subsample, index)

for (i in 1:33) {
  RoachRun_Volume_Post %>%
    filter(index == i) %>%
    select(X, Y, Z) %>%
    as.matrix() %>%
    convhulln("FA") %>%
    print()
}

HalfTire_Volume_Post <- HalfTire_VidSync_Post %>%
  arrange(objects) %>%
  filter(!grepl("Surface_Shots.*", objects)) %>%
  filter(!grepl("^Length.*", event)) %>%
  mutate(subsample = str_extract(objects, "\\d")) %>%
  mutate(index = str_extract(objects, "\\h\\d{1,2}")) %>%
  mutate(species = str_extract(objects, "Omykiss|Okisutch")) %>%
  transform(index = as.numeric(index),
            subsample = as.numeric(subsample)) %>%
  arrange(subsample, index, time) %>%
  select(subsample, index, X, Y, Z) %>%
  arrange(subsample, index)

for (i in 1:48) {
  if (i == 6) {
    next
  }
  if (i == 7) {
    next
  }
  if (i == 8) {
    next
  }
  if (i == 14) {
    next
  }
  if (i == 20) {
    next
  }
  if (i == 29) {
    next
  }
  if (i == 36) {
    next
  }
  if (i == 40) {
    next
  }
  if (i == 41) {
    next
  }
  HalfTire_Volume_Post %>%
    filter(index == i) %>%
    select(X, Y, Z) %>%
    as.matrix() %>%
    convhulln("FA") %>%
    print()
}

vol_test <- RoachRun_Volume_Post %>%
   filter(index == 1) %>%
    select(X, Y, Z) %>%
    as.matrix() %>%
    convhulln("FA") 

print(vol_test$vol)
```
###Overlap in Forage Volumes
Using the 'Hypervolume' package to calculate overlap in occupied volumes by the fish observed in each subsample.

Potential list of tools to use from this package: 
expectation_convex
get_volume
get_centroid


####Pre-Augmentation
```{r}
for (i in 1:13) {
  if (i == 3) {
      next
    }
  if (i == 10) {
      next
    }
    GolfBall_Volume_Pre %>%
      filter(index == i) %>%
      select(X, Y, Z) %>%
      expectation_convex(check.memory = FALSE) %>%
      print()
  }

function()

#look into making a function or creating a list (i.e. list1 = c(HV1, HV2, HV3, etc.) for each forloop scenario)

HV2 <- GolfBall_Volume_Pre %>%
  filter(index == "2") %>%
  select(X, Y, Z) %>%
  as.matrix() %>%
  expectation_convex(check.memory = FALSE)

HV4 <- GolfBall_Volume_Pre %>%
  filter(index == "4") %>%
  select(X, Y, Z) %>%
  expectation_convex(check.memory = FALSE) 

test <- hypervolume_set(HV2, HV4, num.points.max = NULL,
verbose = TRUE, check.memory = FALSE, distance.factor = 1)

str(test)

myvol <- test@HVList$Intersection@Volume

get_volume(HV4)
```
####Post-Augmentation
```{r}

```
